Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-24 main.tex
Improved the abstract to be clearer about testing on subjects and also other better wording.

\abstract{
  Uncontrolled bicycles are generally unstable at low speeds. We add a
  controlled steering motor to a consumer electric bicycle that stabilizes it
  at low speeds. To test the motor's assistance during falls, we apply varying
  magnitude external handlebar perturbations to the bicycle while ridden on a
  treadmill with the balance assist system activated and deactivated. The
  probability of not recovering from a handlebar perturbation decreases when
  the balance assist is activated at a travel speed of 6~\si{\kph}. Use of a
  balance assist system in real world bicycling will reduce the number of falls
  that occur near riders' control authority limits.
}

>>>>

\abstract{
  Uncontrolled bicycles are generally unstable at low speeds. We add an
  automatically controlled steering motor to a consumer electric bicycle that
  has a stabilizing effect down to about 1~\si{\kph}. We hypothesize that a
  stabilized bicycle will reduce the probability of falling. To test the
  motor's possible assistance during falls, we apply varying magnitude external
  handlebar perturbations to twenty-six subjects who rode on a treadmill with
  the balance assist system activated and deactivated. The probability of not
  recovering from a handlebar perturbation significantly decreases when the
  balance assist is activated at a travel speed of 6~\si{\kph}. This positive
  effect is most prominent at and around the individual riders' perturbation
  resistance threshold. We conclude that use of a balance assist system in real
  world bicycling would reduce the number of falls that occur near riders'
  control authority limits.
}
